Associative Data Structures for Website Filtering

### 2014-04-17 paper/paper.tex
Got rid of a footnote.

    For our time measurements, we used libstdc++'s implementation of the standard
    \texttt{std::chrono::high\_resolution\_clock} class.  There is no official documentation about
    the resolution of this clock, but measurements show that it is likely below one microsecond,
    which is sufficient for our purposes.\footnote{\url{http://stackoverflow.com/a/5524138/559931}}

>>>>

    For our time measurements, we used libstdc++'s implementation of the standard
    \texttt{std::chrono::high\_resolution\_clock} class.  There is no official documentation about
    the resolution of this clock, but measurements show that it is likely below one microsecond,
    which is sufficient for our purposes.
